%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage{multicol}
\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[hyperref]{}
\usepackage[scale=0.9]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Wenqing} % Your first name
\familyname{Zong} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
% \address{116 RKB, IIT Roorkee}{Uttarakhand, India 247667}
\mobile{(+44) 07713 918152}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{wenqing.zong98@gmail.com}
% \email{asinha@mt.iitr.ac.in}
% \homepage{sinashish.github.io}{www.sinashish.github.io} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{\href{https://github.com/WenqingZong}{Github: WenqingZong}}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%
%\lipsum[1-2] % Dummy text
%\lipsum[4] % Dummy text
%
%\makeletterclosing % Print letter signature
%
%\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2021 - 2022}{Imperial College London}{\newline MSc.Advanced Computing}{}{}{Final Grade 70+}  % Arguments not required can be left empty

\cventry{2018 - 2021}{The University of Manchester}{\newline BSc.Artificial Intelligence}{}{}{Top 10\% Graduate}  % 
\cventry{2017 - 2018}{INTO Manchester}{\newline Foundation Year}{}{}{Top 10\% Graduate with A*A*A* in Maths, Further Maths and Physics}  %
%\section{%Masters Thesis}

%\cvitem{Title}{\emph{Money Is The Root Of All Evil -- Or Is It?}}
%\cvitem{Supervisors}{Professor James Smith \& Associate Professor Jane Smith}
%\cvitem{Description}{This thesis explored the idea that money has been the cause of untold anguish and suffering in the world. I found that it has, in fact, not.}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

%\subsection{%Vocational}

\cventry{Jan 2023 - Present}{Software Engineer}{Codethink}{Manchester, UK}{}{
\begin{itemize}
\item Developed and contributed to Free and Open-Source Software to automate quality assurance testing.
\item Quality Assurance Deamon: Provides remote interaction with a device in place of having to physically interact with it. It's a remote control for test rigs. \href{https://www.codethink.co.uk/articles/2023/qad-for-hardware-testing/}{[Link to Blog Post]}
\item Testing in a Box: Integrates GitLab server/runner, OpenQA webUI/worker, and Q.A.D. into one box, making it an all-in-one solution for fully automated hardware testing. On-going project.
\item Skills: C, CI/CD, Ansible, Docker, Team communication, Technical writing for documentation and blog post.
\end{itemize}}

\cventry{Jun 2021 - Aug 2021}{Machine Learning Engineer Internship}{AgCIM Research Centre}{Guangzhou, China}{}{
\begin{itemize}
\item Utilized Pytorch to develop an image-based rural area hazard detection system with core functionalities such as object segmentation and road category classification.
\item Improved the accuracy of the road width calculation module in City Information Modeling (CIM) by incorporating the MegaDepth network.
\end{itemize}}

\cventry{Jun 2022 - Aug 2022}{Network Support Engineer - Part Time}{Sobey}{London}{}{
\begin{itemize}
\item Monitored the status of over 200 server clusters and ensure the proper functioning of the database.
\item Regularly performs maintenance on PCs for non-technical colleagues.
\end{itemize}}


\section{Skills}

\cvitem{Languages}{Python, Java, Rust, C, JavaScript, familiar with C++}
\cvitem{Frameworks}{PyTorch, Numpy, Spring, OpenGL, Flask, JUnit}
\cvitem{Utilities}{Linux, Docker, Ansible, Git, Markdown, LaTeX, CI/CD, OpenQA, familiar with AWS}
\cvitem{Communication}{English(fluent), Chinese(mother language)}


\section{Projects}

\cventry{Jun 2023 - Present}{Rust Octree Library}{}{\href{https://github.com/WenqingZong/Octree}{[Code]}}{Rust}{
\begin{itemize}
\item Ongoing personal project.
\item A highly optimised Octree implementation.
\item Capable of tracking dynamic objects in the environment.
\item Easy to integrate into existing codebase.
\end{itemize}}

\cventry{Mar 2023 - May 2023}{Brainf*ck Interpreter in Rust}{}{\href{https://github.com/WenqingZong/BrainfuckInterpreter}{[Code]}}{Rust}{
\begin{itemize}
\item Developed a highly optimized interpreter for the Brainf*ck language using Rust.
\item Implemented a modern and user-friendly command-line interface.
\item Included extensive debugging messages for static checking and runtime errors.
\item Achieved high test coverage and fully documented the project.
\end{itemize}}

\cventry{May 2022 - Sep 2022}{Unsupervised Domain Adaptation on Medical Images}{\textit{Dr.  Matthew Williams, Imperial College London}}{\href{https://github.com/WenqingZong/Momentum-Prototype-UDA}{[Code]}}{PyTorch}{
\begin{itemize}
\item Devised a novel method for addressing the domain shift problem, enabling a model trained on one dataset to adapt and fit to another dataset without significant loss in performance.
\item The proposed novel method offers two key benefits:
\\
1. Source-Free: Model adaptation does not require the source dataset, which enhances cross-institutional collaboration efficiency and addresses data privacy.
\\
2. Supports Various Network Backbones: The novel method is compatible with all neural network architectures, without any special requirements.
\item Demonstrated the efficacy of the proposed method on BraTS2021 dataset, achieving comparable performance with the state-of-the-art approach.
\end{itemize}}

\cventry{Jan 2022 - Mar 2022}{Robot Learning and Control in Maze Environment}{Self-motivated}{PyTorch}{}{
\begin{itemize}
\item Implemented several algorithms to teach a robot how to solve a maze.
\item Traditional algorithm: Cross Entropy Method. Continuously adjusted the covariance matrix to make the action distribution approach the known optimal solution.
\item Machine Learning: Trained a model to learn the non-linear environment and later used in Model Predictive Control algorithm.
\item Behavioural Cloning. Trained a model to mimic how humans navigate in the maze. Implemented the DAgger algorithm to improve the model's performance while reducing the amount of data needed.
\end{itemize}}

\cventry{Oct 2020 - Apr 2021}{Procedural Terrain Generation for Video Game Development}{\textit{Dr Ke Chen, The University of Manchester}}{PyTorch, C\#, Unity}{}{
\begin{itemize}
\item Utilized Perlin noise to procedurally generate terrains for modern RPG games and simulated hydraulic erosion process to enhance playability.
\item Employed Spatial GAN model to generate realistic terrain for a flight simulation game.
\item Completed as a First Class Final Year project for my undergraduate degree.
\end{itemize}}
 
\cventry{Oct 2020 - Dec 2020}{MCTS Board Game AI}{Team}{\href{https://github.com/WenqingZong/Kalah_AI}{[Code]}}{Java}{
\begin{itemize}
\item Collaborated with a team of four to develop an AI bot to play a board game, Kalah.
\item Implemented a bot based on Monte Carlo Tree Search with some improvements such as Early Payout Termination and MCTS-Minimax hybrid.
\item Our bot beats 37 bots submitted by other teams (51 in total) in a tournament.
\end{itemize}}
 
\cventry{Jan 2020 - May 2020}{EventLite Website}{Team}{Java, Spring, JUnit, Jenkins}{}{
\begin{itemize}
\item Lead a team of 6 people to develop a website, EventLite, in Spring framework.
\item Set up and maintained the website database.
\item Code is maintained in a high standard with unit tests and security tests of each function we implemented.
\end{itemize}}

\cventry{Oct 2019 - Jan 2020}{Stendhal Game}{Team}{Java, JUnit, Jenkins}{}{
\begin{itemize}
\item Worked in a group of 7 to maintain an open source game in GitLab. 
\item Fixed bugs raised by players and added JUnit tests for them. Introduced new story-line based on the original game and refactored some hard-to-read legacy code.
\end{itemize}}

\section{Extra Curriculars}

\cventry{Oct 2020 - Mar 2021}{Animal Observer Volunteer}{ZSL Instant Wild}{}{}{
Identified hundreds of animals from photos to promote behaviour analysis, demonstrating a strong attention to detail and the ability to concentrate for extended periods of time.
}

\cventry{Sep 2019 - Jun 2020}{PASS Leader}{The University of Manchester}{}{}{
Helped several first year students in Peer Assisted Study Session, offering academic support and developed interpersonal skills.
}

\cventry{Dec 2019 - Dec 2019}{Panda Volunteer}{China Conservation and Research Center for Giant Panda}{}{}{
Assisted in cleaning panda rooms, preparing their food, and collecting data to monitor their health.
}

\cventry{Sep 2018 - Jun 2019}{Student Representative}{The University of Manchester}{}{}{
Acted on behalf of students to raise concerns and suggestions to department staff, with the aim of making a positive impact on the CS department community.
}

\cventry{Jun 2018 - Aug 2018}{IELTS Teaching Assistant}{DISA English}{}{}{
Assisted nine students in achieving a score of 7 or higher in the reading and listening sections of the IELTS exam.
}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{Interests}

%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

%\cvlistdoubleitem{Cycling}{Hiking}
%\cvlistdoubleitem{Sketching}{Gaming}
%\cvlistitem{Quizzing}
%----------------------------------------------------------------------------------------

% \section{References}

% \begin{multicols}{2}
% \cventry{}{K.S Suresh}{\newline Assistant Professor}{\newline Metallurgical and Materials Engg., IIT Roorkee}{\newline suresfmt@iitr.ac.in}{}
% \columnbreak
% \cventry{}{Anu Chandra}{\newline CEO}{\newline Ryelore AI}{\newline anu@ryelore.com}{ }
% \end{multicols}
%\cventry{}{Arpit Gupta}{\newline VP Engineering}{\newline Antriex IT Services}{\newline arpit.gupta@antmex.com}{}

%\cventry{}{B.S.S Daniel}{\newline Professor}{\newline Metallurgical and Materials Engg., IIT Roorkee}{\newline s4danfmt@iitr.ac.in}{ }
\end{document}